What is long-distance dispersal? And a taxonomy of dispersal events\\ \vspace{2cm}

### 2016-10-11 Manuscript/MS- What is LDD.tex
Final version R1 completed.

{\small \textbf{Manuscript information: }** Words; ** Chars; ** Pages, * Figures; * Tables.}
\end{spacing}

@@

An added difficulty to bridge ecological processes of dispersal with their genetic consequences is the fact that dispersal per se does not necessarily imply realized gene flow \citep{Mallet:2001wx}. Yet in the genetics literature, the inescapable difficulty to robustly estimate $\sigma_x$, the the standard deviation of parent-offspring distances, as an estimate of realized gene flow distance, is analogous to the ecological scenario. Strongly leptokurtic distributions of dispersal distances would lead to severe underestimation of $\sigma_x$, e.g., in mark-recapture studies limited to local sites where the long tail of LDD events escapes detection beyond the edges of the study area \citep{Mallet:2001wx}. Thus, fat-tailed distributions of dispersal distances tend to homogenize distant populations, leading to stronger reductions in $F_{st}$ than expected from local records of dispersal events \citep{Rousset:1997bd}. Despite such difficulties, comparative approaches \citep[e.g.,][]{Bohonak:1999aa} demonstrate that dispersal makes a measurable contribution to population genetic differentiation in most animal species in nature, and that gene flow estimates are rarely so overwhelmed by population history, departures from equilibrium, or other microevolutionary forces as to be uninformative. The relationship between dispersal and realized gene flow is key to understand how migration interacts with drift in driving the dynamics of genetic pools and population differentiation \citep{Garant:2007cka}.

@@

Two important components of plant dispersal ecology concern the movement of propagules away from the source population, a type of dispersal relevant to colonization ability and range expansion \citep{Howe:2004}, and the movement away from the location of close relatives, i.e., a movement away from the genetic neighborhood \citep{Hardesty:2006lr,Jones:2008il}. If we classify dispersal events according to these two spatial frameworks (Table 1) we end up with four distinct types of events depending on whether or not dispersed propagules are disseminated within these reference areas. Setting the limits of a population can be problematic \citep{Waples:2006ev} yet we can identify with relative ease the geographical limits of plant stands, patches, habitat spots or other types of habitat or microhabitat discontinuities that determine landmark boundaries of biological significance \citep[see][for further discussion of boundaries for dispersal]{Kinlan:2005fb}. These "frontiers" set biological limits to what a LDD event is in relation to the geographic limits of the source population. Most plants are distributed as clumped patches, discrete stands, or relatively isolated populations, so we may distinguish between short-distance and long-distance dispersal events that end up with dissemination within or beyond, respectively, the stand or population geographic boundaries (Table 1, $SDD_{loc}$ or $LDD_{loc}$) (Figure 2).

>>>>

{\small \textbf{Manuscript information: } 8979 Words; 37 Pages, 4 Figures; 2 Tables.}
\end{spacing}

@@

An added difficulty to bridge ecological processes of dispersal with their genetic consequences is the fact that dispersal per se does not necessarily imply realized gene flow \citep{Mallet:2001wx}. Yet in the genetics literature, the inescapable difficulty to robustly estimate the the standard deviation of parent-offspring distances, $\sigma_x$ as a proxy for realized gene flow distance, is analogous to the ecological scenario. Strongly leptokurtic distributions of dispersal distances would lead to severe underestimation of $\sigma_x$, e.g., in mark-recapture studies limited to local sites where the long tail of LDD events escapes detection beyond the edges of the study area \citep{Mallet:2001wx}. Thus, fat-tailed distributions of dispersal distances tend to homogenize distant populations, leading to stronger reductions in $F_{st}$ than expected from local records of dispersal events \citep{Rousset:1997bd}. Despite such difficulties, comparative approaches \citep[e.g.,][]{Bohonak:1999aa} demonstrate that dispersal makes a measurable contribution to population genetic differentiation in most animal species in nature, and that gene flow estimates are rarely so overwhelmed by population history, departures from equilibrium, or other microevolutionary forces as to be uninformative. The relationship between dispersal and realized gene flow is key to understand how migration interacts with drift in driving the dynamics of genetic pools and population differentiation \citep{Garant:2007cka}.

@@

Two important components of plant dispersal ecology concern the movement of propagules away from the source population, a type of dispersal relevant to colonization ability and range expansion \citep{Howe:2004}, and the movement away from the location of close relatives, i.e., a movement away from the genetic neighborhood \citep{Hardesty:2006lr,Jones:2008il}. If we classify dispersal events according to these two spatial frameworks (Table 1) we end up with four distinct types of events depending on whether or not dispersed propagules are disseminated within these reference areas. Setting the limits of a population can be problematic \citep{Waples:2006ev} yet we can identify with relative ease the geographical limits of plant stands, patches, habitat spots or other types of habitat or microhabitat discontinuities that determine landmark boundaries of biological significance \citep[see][for further discussion of boundaries for dispersal]{Kinlan:2005fb}. These "frontiers" set biological limits to what a LDD event is in relation to the geographic limits of the source population. Most plants are distributed as clumped patches, discrete stands, or relatively isolated populations, so we may distinguish between short-distance and long-distance dispersal events that end up with dissemination within or beyond, respectively, the stand or population geographic boundaries (Table 1, $SDD_{loc}$ or $LDD_{loc}$) (Fig. 2).
